%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv} 

% Set theme to classic
\moderncvstyle{classic}
% Set color to black
\moderncvcolor{black}

% to set the default font: use '\sfdefault' for the default sans serif font
%                              '\rmdefault' for the default roman one
%                               any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% for the 'classic' style, if you want to force the width allocated to your name
% and avoid line breaks. Be careful though, the length is normally calculated to
% avoid any overlap with your personal info; use this at your own typographical
% risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{Luke}{Hurst}
\address{1114 Prospect Ave. Unit 2}{Ann Arbor, MI 48104}
\phone[mobile]{(989)~277~7714}
\email{hurstlj@umich.edu}

% to show numerical labels in the bibliography (default is to show no labels);
%    only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------

\begin{document}

%-----       letter       ------------------------------------------------------
% recipient data
\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
\date{\today}
\opening{To Whom it May Concern,}
\closing{Sincerely,}
\enclosure[Attached]{resume{}} % use an optional argument to use a string other
                               % than "Enclosure", or redefine \enclname
\makelettertitle

I am writing to apply for the JOB\_TITLE position available at COMPANY\_NAME. As a student at the University of Michigan, in the College of Engineering, I had the opportunity to talk with you at the University’s semi-annual career fair in the fall. [Add in a little personal verbiage here]. I plan to graduate in the spring of 2017 with a Bachelor of Science in Computer Science Engineering. This makes me well suited for the JOB\_TITLE as well as future with COMPANY\_NAME.

Computer Science Engineering coursework will lay a solid foundation for these careers in software design. However, my extracurricular experiences are what demonstrate my potential to succeed as a software engineer. One of these was my time spent with the Undergraduate Research Opportunity Program during my freshman year. I assisted a professor on campus who researched transient objects (things that go bang) in the night sky. I gained experience analyzing data and writing scripts using IDL to supplement her research. Much of this work was done independently and thus I had to demonstrate self-motivation and learn to enforce my own deadlines. Another extracurricular activity I am involved in currently is the Michigan Autonomous Aerial Vehicles project team. Within this team I was asked to contribute solutions and ideas for navigation and computer search algorithms. This experience is giving me the opportunity to solve real life problems and apply the coursework I am currently learning. Both of these extra-curricular activities prepare me well for the JOB\_TITLE.

I have the skills and experience to perform the tasks of JOB\_TITLE to high standards. I can be an asset toward COMPANY\_NAME's future growth and prosperity. I look forward to demonstrating that upon further contact.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
